SoK: Web Application Attack Defenses (in Question)

### 2014-10-07 docs/questioning.tex
better requirements

\begin{equation}
\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 - \textrm{PR})}
\end{equation}

\begin{equation}
\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 - \textrm{PR})}
\end{equation}

@@

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item Reporting of values for True Positives ($a$), False Positives
  ($b$), False Negatives ($c$), True Negatives ($d$), on test
  environments.
\item Reporting of values for True Positives ($A$), False Positives
  ($B$), False Negatives ($C$), True Negatives ($D$), on the
  performance of the mechanism on environments with real attack
  profiles.
\end{itemize}

>>>>

\begin{equation}
\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 -
\textrm{PR})}
\label{eq:ppv-se-sp}
\end{equation}

\begin{equation}
\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 -
\textrm{PR})}
\label{eq:npv-se-sp}
\end{equation}

@@

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item \textbf{Sensitivity, Specificity}: Reporting of values for True
  Positives ($a$), False Positives ($b$), False Negatives ($c$), True
  Negatives ($d$), on test environments.
\item \textbf{\textsc{ppv}, \textsc{npv}}: Reporting of values for True
  Positives ($A$), False Positives ($B$), False Negatives ($C$), True
  Negatives ($D$), on the performance of the mechanism on environments
  with real attack profiles. Alternatively, since from
  equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} \textsc{ppv}
  and \textsc{npv} can be calculated by the sensitity and specifity
  given the prevalence, reporting of prevalance, sensitivity,
  specificity.
\end{itemize}
